Building a continuous benchmarking ecosystem in bioinformatics

### 2024-10-29 manifesto-main.tex
More edits following Mark's comments

\section*{Parameter sweeps}

@@

Parameters can be method-specific, but also dataset-specific, e.g., the true number of clusters when evaluating clustering algorithms. In this case, they can also be seen as (dataset-specific) metadata. To differentiate between the effect of the parameter and the methods performances themselves, data-specific parameters should be shared across methods during evaluation.

Similarly, optimizing parameters for some but not other methods can skew results and should be avoided.

@@

Altogether, evaluating parameters as part of a benchmark can give useful insights, but should be linked to a distinct and independent research objective.

>>>>

\section*{(Hyper)parameters}

@@

Dataset-specific parameters, e.g., the true number of clusters when evaluating clustering algorithms, are not method-specific. In this case, they can also be seen as (dataset-specific) metadata. To differentiate between the effect of the parameter and the methods performances themselves, data-specific parameters should be shared across methods during evaluation.

Similarly, optimizing method-specific parameters for some but not other methods can skew results and should be avoided.

@@
